Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-04-10 manuscript/manuscript.Rmd
Update manuscript.Rmd

  TODO: 
  - Add set_lambda, get_lambda, set_shift, get_shift methods.
  - Add option to set p-value for central normality test. Default NULL (no filtering)
  - implement into familiar

@@

Shift-sensitive power transformations are implemented in the `power.transform` package.

>>>>

  TODO: 
  - Add set_lambda, get_lambda, set_shift, get_shift methods.
  - implement into familiar
  - update familiar.experiment to allow for setting external configurations (or maybe make that the default -- its definitely easier and more transparent.)

  - Add tests for out-of-bound actions (power_transform) and GOF test rejection (find_parameters).

@@

Shift-sensitive power transformations are implemented in the `power.transform` package. This manuscript was created using R Markdown, and is available from [https://github.com/alexzwanenburg/power.transform].
